---
title: "In Class Lab - DIY Functions"
author: "John Esparragoza"
date: "DATA 2401"
output: html_document
---

**Note: Your exam will be in a similar format to this (RMarkdown File with Questions and Code chunks for your answers), so make sure you have the process for knitting to html working.**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In Class Activity

The questions from your notes today are below, please copy your answers them here! Then complete the two new tasks, and attempt the "hard mode" if you have time.

1.  Write your own function that takes the temperature in Fahrenheit as an argument and returns the Celsius equivalent.

```{R}
f_to_c <- function(f_temp) {
  c_temp <- (f_temp - 32) * 5/9
  return(c_temp)
}
f_to_c(212)
```

2.  Expand that function so that it takes a temperature in Fahrenheit and a distance in feet and returns **both** the temperature in Celcius and the distance in meters (you'll likely need to remember the `c()` function!)

```{r}
conversions <- function(f_temp, distance_f) {
  c_temp <- (f_temp - 32) * 5/9
  distance_m <- distance_f / 3.281
  return(c(c_temp, distance_m))
}

conversions(32, 3)
```

3.  Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0.

```{R}
num <- function(number){
if (number > 0) {
  print("number is positive")
} else if(number < 0) {
  print("number is negative")
} else if(number == 0) {
  print("number is 0")
}
}

num(4)
```

4.  Write a function that returns the absolute value of the number passed as an argument.
    -   Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary.

```{r}
abs_val <- function(num){
  if (num > 0)
    num
  else
  num * -1
}

abs_val(-6)
abs_val(4)
```

5.  Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string.
    -   There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here

```{r}
abs_val <- function(num) {
  if (is.character(num))
  print("error")
  else if (num > 0)
    num
  else
  num * -1
}

abs_val(-4)
abs_val(4)
abs_val("none")
```

\`\`\`
